Regular singular Volterra equations on complex domains

### 2023-08-31 reg-sing-volterra.tex

Our main result is to show that for a certain kind of regular singular Volterra equation on a complex domain, there is always a unique solution of a certain form. As a motivating example, this kind of Volterra equation arises when using Laplace transform methods to solve a {\em level~1} differential equation.
\end{abstract}

\tableofcontents

\begin{brainstorm}
\item \textcolor{gray}{\textbf{(Veronica)} Deal with Condition~\eqref{cond:sing}}
\begin{itemize}
\item \textcolor{gray}{In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?} \textcolor{MediumSpringGreen}{[Yes.]}
\item \textcolor{gray}{Rewrite arguments using new Condition~\eqref{cond:sing}.}
\item \textcolor{gray}{Show that example satisfies Condition~\eqref{cond:sing}.}
\end{itemize}
\item \textcolor{gray}{\textbf{(Aaron)} Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}}
\begin{itemize}
  \item \textcolor{gray}{Add a condition to ensure that $\zeta(a) = 0$ is the only singularity.}
  \item \textcolor{gray}{Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.}
  \item \textcolor{gray}{When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.} \textcolor{MediumSpringGreen}{[No change required]}
  \item \textcolor{gray}{Refer to Condition~\eqref{cond:diag-basic} in proof of Theorem~\ref{thm:proto-growth}.}
  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSpringGreen}{[No other direct references found.]}
\end{itemize}
\item \textcolor{gray}{\textbf{(Veronica)} Make sure that everything is switched to the new Condition~\eqref{cond:diag-basic}.}
\textcolor{gray}{
\item Set $R_1, \ldots, \ldots R_{d-1}$ to zero.
\begin{itemize}
\item Change definition.
\item Change intro to clarify that our results only apply to some level~1 equations.
\item Change intro to clarify that our results only apply to some level~1 equations.
\end{itemize}}
\item \textcolor{gray}{\textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.}
\begin{itemize}
    \item \textcolor{gray}{Proofread and drop old version.}
\end{itemize}
\item \textcolor{gray}{\textit{(Aaron)} Finish introduction}
\begin{itemize}
\item \textcolor{gray}{\textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.}
\item \textcolor{gray}{\textit{(Veronica)} Revise introduction, if desired.}
\end{itemize}
\color{gray}
\item \textit{(Veronica)} Say in Section~\ref{setting:perturbed} that $\volterra = \hardpart + \softpart$ and write arguments we need for bounds on whole kernel (for example, in Equation~\ref{near-limit}.
\color{gray}
\item \textit{(Veronica)} Review old blue text in Section~\ref{setting:perturbed} and decide whether we want to keep any of it. Can drop unilaterally. 
\color{violet}
\item Revise stuff related to proof of main results.
\begin{itemize}
        \item \textcolor{gray}{\textit{(Aaron)} Add proof of Lemma~\ref{lem:perturbed_volterra} to Section~\ref{sec:existence and uniqueness}}
        \item \textcolor{gray}{\textit{(Aaron)} Revise proof of Theorem~\ref{thm:general_volterra} in Section~\ref{sec:existence and uniqueness}}
        \begin{itemize}
            \item \textcolor{gray}{Proofread revised proof.}
        \end{itemize}
        \item \textcolor{gray}{\textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.}
        \color{gray}
        \item \textit{(Veronica)} Add motivation to Section~\ref{sec:image under soft_part}, explaining that the desired result of the section follows from a more general result about the smoothing effect of $\softpart$ (Proposition~\ref{prop:smoothing}). \textcolor{green}{I added a Corollary to explicitly write how Proposition \ref{prop:smoothing} implies the regularity we want for $\softpart f_0$}
        \color{violet}
        \item \textbf{(Aaron)} Confirm again that removed $\tau+\gamma$ upper bound on $\rho$ was unnecessary.
\end{itemize}
\item \textcolor{gray}{Revise text around main results.}
\begin{itemize}
    \item \textcolor{gray}{Decide whether to keep Lemma~\ref{lem:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary. Change order as appropriate.} \textcolor{purple}{Keep Lemma~\ref{lem:perturbed_volterra} as a lemma. State it after Theorem~\ref{thm:general_volterra}.}
    \color{gray}
    \item \textit{(Veronica)} Convert ``proof'' blocks to plain prose after main results. 
\end{itemize}
\color{gray}
\item \textbf{(Veronica)} Edit statement of Theorem~\ref{thm:example} 
\begin{itemize}
    \item Edit or remove statements about making $\Lambda$ big enough
    \item Figure out how to clean up $Q(-\zeta')$ business
\end{itemize}
\color{violet}
\item \textcolor{gray}{Start finalizing notation for the two parts of the operator and the two parts of the solution.}
\begin{itemize}
    \item \textcolor{gray}{Choose subscripts or decorations to tell things apart in equations.} \textcolor{gray}{Change $\hardpart$ with $\volterra_0$ and $\softpart$ with $\volterra_\star$. Same for $\hardker$ and $\softker$.}
    \item \textcolor{gray}{Choose names to tell things apart in prose. Currently using ``prototypical operator,'' ``prototype solution.'' Come up with names for perturbation stuff.}
\end{itemize}
\item \textbf{(Aaron)} Read through Section~\ref{sec:example}.
\color{gray}
\item \textbf{(Veronica)} Consider revising notation for roots. 
\begin{itemize}
\item ``$P$ is a monic degree-$d$ polynomial with only simple zeros;''
\item ``$Q$ is a degree-$(d-1)$ polynomial, and $Q(-\alpha) \neq 0$ for for every zero $-\alpha$ of $P$;''---or even say it without formulas.
\end{itemize}
\color{violet}
\item \textcolor{gray}{\textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.}
\item \textcolor{gray}{Work on acknowledgements}
\begin{itemize}
\item \textcolor{gray}{\textbf{(Aaron)} Add people Aaron had conversations with}
\item \textcolor{gray}{\textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).}
\end{itemize}
\item \textcolor{gray}{Reconsider using $\lesssim$ (but still leaning not to)}
\begin{itemize}
    \item \textcolor{gray}{\textbf{(Aaron)} As an example, show how we could rewrite the argument in proof of Proposition~\ref{prop:asymptotic at infinity} with $\lesssim$.}
\end{itemize}
\item \textcolor{gray}{Write abstract.}
\item \textcolor{gray}{\textbf{(Veronica)} Add table of contents.}
\item \textcolor{gray}{Replace $\psi_0$ with $\chi$.}
\item \textcolor{gray}{Replace $\epsilon$ with $\gamma$.}
\item \textcolor{gray}{\textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)}
\end{brainstorm}
\section{Introduction}\label{sec:intro}
\subsection{Motivation}\label{motivation}
In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$. Write $z$ in terms of its real and imaginary parts as $x + iy$. Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it. Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
\frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
z^{-\lambda} \laplace \varphi & = \laplace\,\partial^{-\lambda} \varphi,
where $\partial^{-\lambda}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.

@@

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{conditions}
\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we'll require, for simplicity, to be real and positive---the difference
\[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.
In addition, for each $\sigma > \tau$, the bound
\[ \big|\hardker(a, a')\big| < \frac{\sigma}{|\zeta(a)|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. 
\end{conditions}
For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$. We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal. These requirements can be combined into one condition.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} For some constant $\lambda_\Delta$, we have
\[ \big| \hardker(a, a') \big| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$. 
%\color{Tomato}
%Furthermore, Condition \eqref{cond:diag-basic} tells us that for any $\sigma>0$ we can find a neighbourhood of $(0,0)\in\domain^2$ where 
%\[|\hardker(a,a')|\le\frac{\sigma}{|\zeta(a)|}.\]
\begin{verify}
    By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ \big| \hardker(a, a') \big| \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
then setting $\delta=\frac{\log(\sigma/c)}{2\lambda_\Delta}$, we deduce that for every $|\zeta(a)|\le\delta$ and  $|\zeta(a')|\le\delta$
\begin{align*}
    |\hardker(a,a')|&\le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta(|\zeta(a)|+|\zeta(a')|)}\\
    &\frac{c}{|\zeta(a)|} e^{2\lambda_\Delta \delta}\\
    &=\frac{\sigma}{|\zeta(a)|}
\end{align*}
\end{verify}
\color{black}
We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
\begin{conditions}
\condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
For some non-zero constant $B$ and some $\epsilon > 0$,
\[ p \in B\zeta + O\big(|\zeta|^{1 + \epsilon}\big) \]
at $\zeta = 0$.
\end{conditions}
\subsubsection{The perturbed operator}\label{setting:perturbed}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{conditions}
\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} For some constant $\gamma > 0$, we have
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{conditions}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

@@

Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
\[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
in $\domain_\text{near}$. It follows that the improper integral
\[ \eta(a) = \int_{\zeta = 0}^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta \]
converges for all $a \in \domain$, allowing us to write
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
Observing that $|\eta| \le C |\zeta|$ in $\domain_\text{near}$, we can conclude that
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
at $\zeta(a) = 0$.

Combining the arguments above, we learn that
\begin{align*}
\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
\end{align*}
at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
\end{proof}
\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we'll show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$. This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
%\par\color{RoyalBlue}
%In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.\color{black}

@@

whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]

@@

\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]

@@

Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Choose a subset $\domain_\text{far} \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have

@@

over all $a \in \domain_\text{far}$ and $a' \in \domain$.

@@

Find a radius $\delta > 0$ with $|\zeta| \ge \delta$ on $\domain_\text{far}$, and choose some $\lambda > \lambda_\Delta$. Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} tell us that

@@

over all $a \in \domain_\text{far}$ and $a' \in \domain$. Since

@@

over all $a \in \domain_\text{far}$ and $a' \in \domain$. This simplifies to the desired result.

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)\,\varphi\;d\zeta| \]

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
& = \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|

@@

\|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
& \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]

>>>>

Our main result is to show that for a certain kind of regular singular Volterra equation on a complex domain, there is always a unique solution of a certain form. As a motivating example, this kind of Volterra equation arises when using Laplace transform methods to solve a {\em level~1} differential equation.
\end{abstract}
\tableofcontents
\section{Introduction}\label{sec:intro}
\subsection{Motivation}\label{motivation}
In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$. Write $z$ in terms of its real and imaginary parts as $x + iy$. Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it. Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
\begin{align*}
\frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
z^{-\lambda} \laplace \varphi & = \laplace\,\partial^{-\lambda} \varphi,
\end{align*}
where $\partial^{-\lambda}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.

@@

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{conditions}
\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we'll require, for simplicity, to be real and positive---the difference
\[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.
In addition, for each $\sigma > \tau$, the bound
\[ |\hardker(a, a')| < \frac{\sigma}{|\zeta(a)|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. 
\end{conditions}
For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$. We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal. These requirements can be combined into one condition.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} For some constant $\lambda_\Delta$, we have
\[ |\hardker(a, a')| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$. 
%\color{Tomato}
%Furthermore, Condition \eqref{cond:diag-basic} tells us that for any $\sigma>0$ we can find a neighbourhood of $(0,0)\in\domain^2$ where 
%\[|\hardker(a,a')|\le\frac{\sigma}{|\zeta(a)|}.\]
\begin{verify}
    By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ | \hardker(a, a') | \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
then setting $\delta=\frac{\log(\sigma/c)}{2\lambda_\Delta}$, we deduce that for every $|\zeta(a)|\le\delta$ and  $|\zeta(a')|\le\delta$
\begin{align*}
    |\hardker(a,a')|&\le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta(|\zeta(a)|+|\zeta(a')|)}\\
    &\frac{c}{|\zeta(a)|} e^{2\lambda_\Delta \delta}\\
    &=\frac{\sigma}{|\zeta(a)|}
\end{align*}
\end{verify}
\color{black}
We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
\begin{conditions}
\condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
For some non-zero constant $B$ and some $\epsilon > 0$,
\[ p \in B\zeta + O\big(|\zeta|^{1 + \epsilon}\big) \]
at $\zeta = 0$.
\end{conditions}
\subsubsection{The perturbed operator}\label{setting:perturbed}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{conditions}
\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} For some constant $\gamma > 0$, we have
\[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{conditions}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

@@

Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
\[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
in $\domain_\text{near}$. It follows that the improper integral
\[ \eta(a) = \int_{\zeta = 0}^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta \]
converges for all $a \in \domain$, allowing us to write
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
Observing that $|\eta| \le C |\zeta|$ in $\near$, we can conclude that
\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
at $\zeta(a) = 0$.

Combining the arguments above, we learn that
\begin{align*}
\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
\end{align*}
at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
\end{proof}
\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we'll show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$. This is a consequence of the general smoothing effect of $\softpart$, described in the following result.

@@

whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Now, we'll show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]

@@

\[ | \softker(a, a') | \lesssim\frac{(2\delta)^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]

@@

Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Choose a subset $\far \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have

@@

over all $a \in \far$ and $a' \in \domain$.

@@

Find a radius $\delta > 0$ with $|\zeta| \ge \delta$ on $\far$, and choose some $\lambda > \lambda_\Delta$. Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} tell us that

@@

over all $a \in \far$ and $a' \in \domain$. Since

@@

over all $a \in \far$ and $a' \in \domain$. This simplifies to the desired result.

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
& = \|\varphi\|_{\rho-1, \Lambda}  \int_0^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|

@@

\|\varphi\|_{\rho-1, \Lambda}  \int_0^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_0^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]
